X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on conventional sources

### 2013-10-24 hedpc_natphys.tex
Added analyzer based on tube citations
    - added appeal letter in pdf
    - added point by point response pdf

%% Packages
\usepackage[utf8]{inputenc} %Umlaute
\usepackage{babel}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[bf,small,labelsep=period]{caption}
\usepackage{graphicx}  %figures
\usepackage[detect-all]{siunitx}

\addto\captionsenglish{\renewcommand{\figurename}{Figure}}
%% New commands
\newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
\DeclareSIUnit{\peak}{p}

@@

X-ray radiography and \ac{CT} are standard imaging techniques in
materials and life sciences for the nondestructive examination of samples or
the diagnosis of diseases in patients. The underlying contrast mechanism
relies on the different X-ray attenuation properties of different materials
or tissue types. The dominant physical effects contributing to attenuation
are the photoelectric effect and incoherent (Compton) scattering. Besides attenuation, the wave
nature of X-rays reveals another contrast mechanism, which is the phase
shift. The interaction contributing to phase shifts is coherent (Rayleigh)
scattering \cite{Als-Nielsen2011}.

@@

Phase-sensitive
imaging is a desirable modality, as it can provide a complementary source of
contrast with respect to absorption by providing direct access 
to the electron density \cite{Als-Nielsen2011}. Moreover, the combination with
attenuation enables the determination of the effective atomic
number \cite{Qi2010}.
An enhanced
\ac{CNR} in images compared to attenuation for certain
materials or tissues \cite{Pfeiffer2007a,McDonald2009} has also been
demonstrated.

The vast majority of phase-sensitive techniques, including crystal analyzer based
\cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Inline
phase contrast \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a} need high
spatial coherence but are available on microfocus sources.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with coded
apertures \cite{Munro2012} and Talbot-Lau interferometry \cite{Pfeiffer2006}.
In addition to phase sensitivity, these techniques provide a dark-field
contrast, also called scatter contrast or visibility-reduction contrast,
that is proportional to the integrated local small angle scattering power
from microscopic density fluctuations in a specimen\cite{Pfeiffer2008}.

Talbot interferometry has been demonstrated using a synchrotron source at
$\SI{82}{\kilo\electronvolt}$\cite{Willner2013} and
$\SI{123}{\kilo\electronvolt}$\cite{Ruiz2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied at $\SI{60}{\kilo\electronvolt}$ mean energy \cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or \ac{CT} require energies between $100$ and
$\SI{150}{\kilo\volt\peak}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

Here, we introduce a method for phase-contrast imaging which is
compatible with the entire diagnostic energy range of X-rays, 
compact imaging arrangements and 
conventional X-ray tubes. The method is based on Talbot-Lau interferometry
\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
arrangement. 
The challenge which limited the progress towards higher energies was mainly
related to the manufacturing of gratings with high aspect ratios. The aspect
ratio, given by
\begin{equation}
    \text{R} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the  structure
height, is normally limited by the lithographic process, as grating
structures tend to collapse or deform (e.g. due to capillary forces) if
the aspect ratio is too high. For a given setup length these parameters
depend on the target energy $E$ according to $p \propto
1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
for the absorption grating around $\textnormal{R}=30$ is necessary for a
reasonable length of the experimental arrangement, it would have to be at
least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, which requires even higher aspect ratios.
The maximum achievable aspect ratios of current fabrication techniques
\cite{David2007,Kenntner2010} are around 60.

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Figure~\ref{Fig:grating_mask}. Each grating resides on a
silicon chip and has its specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy \cite{David2002}. Using
gold as the phase shifting material, this requires a structure length of
$h_1 = \SI{19.8}{\micro \metre}$. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter \cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can sufficiently attenuate X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
separated at the first fractional Talbot order \cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure} [ht]
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and \ac{SEM}
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The \ac{SEM} image shows the gold structures and the interrupting bridges
        that prevent the lamellae from collapsing\cite{Kenntner2010}.}
        \label{Fig:grating_mask}
\end{figure}

Due to the high spectral acceptance \cite{Weitkamp2005,Thuering2013c} of the
interferometer ($\SI{50}{\kilo\electronvolt}$ to
more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
the source and analyzer gratings ($>90\%$ up to
$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
approximately $\SI{100}{\micro \metre}$, the field of view in the vertical
direction is limited to one detector pixel row. In the horizontal direction,
the field of view is limited by the grating size and the geometric
magnification of the sample, yielding a maximum field of view of
$\SI{30}{\milli\metre}$. In addition to the standard components (source,
camera, interferometer), two optical slits, one in front of the source
grating, the other in front of the camera, were required for the collimation
of the beam in the vertical direction.

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resuluting in lower absorption contrast. Due to the weaker energy
dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening \cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase nature in
high energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.
\begin{figure}[ht]
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}
    \label{Fig:img_chip}
\end{figure}

Edge-on illuminated grating interferometry breaks the current limitations of
phase-contrast imaging to the lower diagnostic energy range. Compact
geometries  using conventional X-ray sources for design energies well above
$\SI{100}{\kilo\electronvolt}$ could be realized with the approach. This
enables the examination of materials of higher density or thickness which
would be opaque at lower energies. Finally, the approach is not
limited to X-ray imaging, but could be easily applied to other grating-based
imaging modalities (e.g., with neutrons \cite{Grunzweig2008}) where high
aspect ratios are required.

\section*{Methods}
Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process \cite{Kenntner2010}. Each grating
resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
grating chips are fabricated on a single 4 inch silicon wafer. The
experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
is a symmetric Talbot-Lau interferometer with a grating period of $p =
\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
grating is positioned $\SI{23}{\centi\metre}$ away from the source.

@@

\section*{Acknowledgements}
We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
Scherrer Institute (PSI), Switzerland, for the
work on the mechanical design, the scientific advice, and the SEM images
respectively, Joachim Schulz and Marco Walter from
Microworks GmbH, Germany, for the competent support on grating design
issues, Christian Kottler and Vincent Revol from Centre Suisse
d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
discussions on the design of the system. This work has been partially
supported by the Competence Centre for Materials Science and Technology
(CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.

@@

\begin{thebibliography}{26}%

@@

@@

\bibitem [{\citenamefont {Stutman}\ and\ \citenamefont
  {Finkenthal}(2012)}]{Stutman2012a}%
  {Stutman}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Finkenthal}},\ }\href {\doibase 10.1063/1.4748882} {\bibfield  {journal}
  {\bibinfo  {journal} {Applied physics letters}\ }\textbf {\bibinfo {volume}
  {101}},\ \bibinfo {pages} {91108} (\bibinfo {year} {2012})}\BibitemShut

@@

>>>>

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc} %Umlaute
\usepackage{babel}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[bf,small,labelsep=period]{caption}
\usepackage{graphicx}  %figures
\usepackage[detect-all]{siunitx}

\addto\captionsenglish{\renewcommand{\figurename}{Figure}}
%% New commands
\newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
\DeclareSIUnit{\voltpeak}{Vp}

@@

X-ray radiography and \ac{CT} are standard imaging techniques in
materials and life sciences for the nondestructive examination of samples or
the diagnosis of diseases in patients. The underlying contrast mechanism
relies on the different X-ray attenuation properties of different materials
or tissue types. The dominant physical effects contributing to attenuation
are the photoelectric effect and incoherent (Compton) scattering. Besides attenuation, the wave
nature of X-rays reveals another contrast mechanism, which is the phase
shift. The interaction contributing to phase shifts is coherent (Rayleigh)
scattering~\cite{Als-Nielsen2011}.

@@

Phase-sensitive
imaging is a desirable modality, as it can provide a complementary source of
contrast with respect to absorption by providing direct access 
to the electron density~\cite{Als-Nielsen2011}. Moreover, the combination with
attenuation enables the determination of the effective atomic
number~\cite{Qi2010}.
An enhanced
\ac{CNR} in images compared to attenuation for certain
materials or tissues~\cite{Pfeiffer2007a,McDonald2009} has also been
demonstrated.

The vast majority of phase-sensitive techniques, including crystal analyzer
based~\cite{Davis1995,Chapman1997} or interferometric~\cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Inline
phase contrast~\cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry~\cite{Cloetens1997,David2002,Momose2003a} need high
spatial coherence but are available on microfocus sources.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with coded
apertures~\cite{Munro2012} and Talbot-Lau
interferometry~\cite{Pfeiffer2006}. Analyzer-based systems have been
recently extended to tube sources~\cite{Nesch2009,Parham2009}
but the photon energy is limited
to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}.
In addition to phase sensitivity, these techniques provide a dark-field
contrast, also called scatter contrast or visibility-reduction contrast,
that is proportional to the integrated local small angle scattering power
from microscopic density fluctuations in a specimen~\cite{Pfeiffer2008}.

Talbot interferometry has been demonstrated using a synchrotron source at
$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013} and
$\SI{123}{\kilo\electronvolt}$~\cite{Ruiz2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or \ac{CT} require energies between $100$ and
$\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

Here, we introduce a method for phase-contrast imaging which is
compatible with the entire diagnostic energy range of X-rays, 
compact imaging arrangements and 
conventional X-ray tubes. The method is based on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
arrangement. 
The challenge which limited the progress towards higher energies was mainly
related to the manufacturing of gratings with high aspect ratios. The aspect
ratio, given by
\begin{equation}
    \text{R} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the  structure
height, is normally limited by the lithographic process, as grating
structures tend to collapse or deform (e.g. due to capillary forces) if
the aspect ratio is too high. For a given setup length these parameters
depend on the target energy $E$ according to $p \propto
1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
for the absorption grating around $\textnormal{R}=30$ is necessary for a
reasonable length of the experimental arrangement, it would have to be at
least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, which requires even higher aspect ratios.
The maximum achievable aspect ratios of current fabrication techniques~\cite{David2007,Kenntner2010} are around 60.

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Figure~\ref{Fig:grating_mask}. Each grating resides on a
silicon chip and has its specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can sufficiently attenuate X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure} [ht]
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and \ac{SEM}
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The \ac{SEM} image shows the gold structures and the interrupting bridges
        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}
        \label{Fig:grating_mask}
\end{figure}

Due to the high spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
interferometer ($\SI{50}{\kilo\electronvolt}$ to
more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
the source and analyzer gratings ($>90\%$ up to
$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
approximately $\SI{100}{\micro \metre}$, the field of view in the vertical
direction is limited to one detector pixel row. In the horizontal direction,
the field of view is limited by the grating size and the geometric
magnification of the sample, yielding a maximum field of view of
$\SI{30}{\milli\metre}$. In addition to the standard components (source,
camera, interferometer), two optical slits, one in front of the source
grating, the other in front of the camera, were required for the collimation
of the beam in the vertical direction.

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resuluting in lower absorption contrast. Due to the weaker energy
dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase nature in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.
\begin{figure}[ht]
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}
    \label{Fig:img_chip}
\end{figure}

Edge-on illuminated grating interferometry breaks the current limitations of
phase-contrast imaging to the lower diagnostic energy range. Compact
geometries  using conventional X-ray sources for design energies well above
$\SI{100}{\kilo\electronvolt}$ could be realized with the approach. This
enables the examination of materials of higher density or thickness which
would be opaque at lower energies. Finally, the approach is not
limited to X-ray imaging, but could be easily applied to other grating-based
imaging modalities (e.g., with neutrons~\cite{Grunzweig2008}) where high
aspect ratios are required.

\section*{Methods}
Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
grating chips are fabricated on a single 4 inch silicon wafer. The
experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
is a symmetric Talbot-Lau interferometer with a grating period of $p =
\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
grating is positioned $\SI{23}{\centi\metre}$ away from the source.

@@

\section*{Acknowledgements}
We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
Scherrer Institute (PSI), Switzerland, for the
work on the mechanical design, the scientific advice, and the \ac{SEM} images
respectively, Joachim Schulz and Marco Walter from
Microworks GmbH, Germany, for the competent support on grating design
issues, Christian Kottler and Vincent Revol from Centre Suisse
d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
discussions on the design of the system. This work has been partially
supported by the Competence Centre for Materials Science and Technology
(CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.

@@

\begin{thebibliography}{29}%

@@

\bibitem [{\citenamefont {Nesch}\ \emph {et~al.}(2009)\citenamefont {Nesch},
  \citenamefont {Fogarty}, \citenamefont {Tzvetkov}, \citenamefont {Reinhart},
  \citenamefont {Walus}, \citenamefont {Khelashvili}, \citenamefont
  {Muehleman},\ and\ \citenamefont {Chapman}}]{Nesch2009}%
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
  {Nesch}}, \bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont {Fogarty}},
  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Tzvetkov}}, \bibinfo
  {author} {\bibfnamefont {B.}~\bibnamefont {Reinhart}}, \bibinfo {author}
  {\bibfnamefont {a.~C.}\ \bibnamefont {Walus}}, \bibinfo {author}
  {\bibfnamefont {G.}~\bibnamefont {Khelashvili}}, \bibinfo {author}
  {\bibfnamefont {C.}~\bibnamefont {Muehleman}}, \ and\ \bibinfo {author}
  {\bibfnamefont {D.}~\bibnamefont {Chapman}},\ }\href {\doibase
  10.1063/1.3213621} {\bibfield  {journal} {\bibinfo  {journal} {The Review of
  scientific instruments}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages}
  {093702} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Parham}\ \emph {et~al.}(2009)\citenamefont {Parham},
  \citenamefont {Zhong}, \citenamefont {Connor}, \citenamefont {Chapman},\ and\
  \citenamefont {Pisano}}]{Parham2009}%
  {Parham}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zhong}},
  \bibinfo {author} {\bibfnamefont {D.~M.}\ \bibnamefont {Connor}}, \bibinfo
  {author} {\bibfnamefont {L.~D.}\ \bibnamefont {Chapman}}, \ and\ \bibinfo
  {author} {\bibfnamefont {E.~D.}\ \bibnamefont {Pisano}},\ }\href
  {http://linkinghub.elsevier.com/retrieve/pii/S1076633209001366?showall=true}
  {\enquote {\bibinfo {title} {{Design and Implementation of a Compact Low-Dose
  Diffraction Enhanced Medical Imaging System}},}\ } (\bibinfo {year}
  {2009})\BibitemShut {NoStop}%

@@

@@

\bibitem [{\citenamefont {Raupach}\ and\ \citenamefont
  {Flohr}(2011)}]{Raupach2011}%
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Raupach}}\ and\ \bibinfo {author} {\bibfnamefont {T.~G.}\ \bibnamefont
  {Flohr}},\ }\href {\doibase 10.1088/0031-9155/56/7/020} {\bibfield  {journal}
  {\bibinfo  {journal} {Physics in medicine and biology}\ }\textbf {\bibinfo
  {volume} {56}},\ \bibinfo {pages} {2219} (\bibinfo {year}
  {2011})}\BibitemShut {NoStop}%
